\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Change alert block colors
%%% 1- Block title (background and text)
\setbeamercolor{block title alerted}{fg=mDarkTeal, bg=mLightBrown!45!yellow!45}
\setbeamercolor{block title example}{fg=magenta!10!black, bg=mLightGreen!60}
%%% 2- Block body (background)
\setbeamercolor{block body alerted}{bg=mLightBrown!25}
\setbeamercolor{block body example}{bg=mLightGreen!15}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
\usepackage{pxrubrica}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{If I had a lot of money, I would buy a big house.}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%
\section{If S $+$ 仮定法過去($=$ V)}

\begin{frame}[plain]{If S $+$ 仮定法過去($=$ V)}
 \large
\begin{enumerate} 
 \item I wish I \textcolor{Maroon}{\bfseries had} money.\hfill{\scriptsize お金があったらいいのに}
 \item If I \textcolor{Maroon}{\bfseries had} money, I would buy the cake.\hfill{\scriptsize お金があったらそのケーキを買うのに}
 \item If I \textcolor{NavyBlue}{\bfseries have} money, I will buy the cake.\hfill{\scriptsize お金があったらそのケーキを買います}
\end{enumerate}


\begin{block}{If S $+$ 仮定法過去($=$ V)}
\small
\begin{itemize}\setbeamertemplate{items}[square]
 \item ifと仮定法過去を組み合わせることがあります\par
If $\text{S}_{1} +$ \myAnch{mood1}{white}{仮定法過去}($= \text{V}_{1}$) \ldots \hspace{2pt},\hspace{10pt}
 $\text{S}_{2}\,+$ \Circled[fill color = white]{\,\,$\left\{ \begin{array}{l}
\text{would} \\
\text{could}
\end{array}\right\} + \text{原形}$\,\,}\,($=\text{V}_{2}$) \ldots\hspace{2pt} .\\[10pt]
\hfill{}\myAnch{mood2}{white}{現在の事実の反対}を表しています
\end{itemize}

\hfill{\scriptsize wouldは「（～なら）～するのに」、couldは「（～なら）～できるのに」の意味になります}

\hfill{\scriptsize would, couldはそれぞれwill, canの過去形です}
 
\begin{tikzpicture}[remember picture,overlay]
 \draw[thick,orange,->] (mood2.west) to[out=180, in=-45] (mood1.south east);
\end{tikzpicture}

\end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
 日本文の意味になるように、適切なものを選びましょう

\begin{enumerate}
 \item 1,000円あったら、チーズバーガーとフライドポテトを買うのに（残念なことに手持ちがない）\\
If I ( get / have / \alt<2->{\Circled{had}}{had} ) 1,000 yen, I would buy a cheeseburger and fries.
 \item もしわたしがあなたなら、毎日朝食を食べますよ\\
If I ( am / are / \alt<3->{\Circled{were}}{were} ) you, I would eat breakfast every day. 
 \item もしわたしがあなたなら、早く寝ますよ\\
If I were you, I ( \alt<4->{\Circled{would}}{would} / will ) go to bed early.
\item もしわたしが魚だったら、じょうずに泳げるのに\\
If I were a fish, I ( can /  \alt<5->{\Circled{could}}{could} ) swim well.
\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
日本文の意味になるよう(~~~~~~~~)内の語句を並べ替えましょう
 \begin{enumerate}
  \item わたしがあなたなら、その本を読みますよ\\
If ( read / you / I / I / the book / were / would  ).\\
\visible<2->{If I were you, I would read the book.}
  \item たくさんお金があったら、大きな家を買うのになあ\\
If ( house / a /would / had / buy / money / I / I / large / a lot of ).\\
\visible<3->{If I had a lot of money, I would buy a large house.}
  \item きょう晴れていたら、外で遊べるのになあ\hfill{\scriptsize outdoors: 屋外で}\\
If ( sunny / I / it / play outdoors / were / could / today ).\\
\visible<4->{If it were sunny today, I could play outdoors.}

 \end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{まとめ}
 \begin{block}{If S $+$ 仮定法過去($=$ V)}
\small
\begin{itemize}\setbeamertemplate{items}[square]
 \item ifと仮定法過去を組み合わせることがあります\par

If $\text{S}_{1} +$ \myAnch{mood1}{white}{仮定法過去}($= \text{V}_{1}$) \ldots\,\,\,,\hspace{10pt}
 $\text{S}_{2}\,+$ \Circled[fill color = white]{\,\,$\left\{ \begin{array}{l}
\text{would} \\
\text{could}
\end{array}\right\} + \text{原形}$\,\,}\,($=\text{V}_{2}$) \ldots\,\,\,.\\[10pt]
\hfill{}\myAnch{mood2}{white}{現在の事実の反対}を表しています
\end{itemize}

\hfill{\scriptsize wouldは「（～なら）～するのに」、couldは「（～なら）～できるのに」の意味になります}

\hfill{\scriptsize would, couldはそれぞれwill, canの過去形です}

 
\begin{tikzpicture}[remember picture,overlay]
 \draw[thick,orange,->] (mood2.west) to[out=180, in=-45] (mood1.south east);
\end{tikzpicture}

\end{block}
\end{frame}
\end{document}
