\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Change alert block colors
%%% 1- Block title (background and text)
\setbeamercolor{block title alerted}{fg=mDarkTeal, bg=mLightBrown!45!yellow!45}
\setbeamercolor{block title example}{fg=magenta!10!black, bg=mLightGreen!70}
%%% 2- Block body (background)
\setbeamercolor{block body alerted}{bg=mLightBrown!25}
\setbeamercolor{block body example}{bg=mLightGreen!15}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{She was listening to the radio.}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


\begin{frame}[plain]
  \titlepage
\end{frame}


\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}

\section{過去進行形}

\subsection{過去進行形とは}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{過去進行形}
 \begin{enumerate}
 \item \visible<1->{She \textcolor{ForestGreen}{\bfseries is sleeping} now. {\small 彼女はいま眠っています。\hfill{}(現在進行形)}}
\visible<2->{\signchart[width=10]{,,{\textcolor{ForestGreen}{いま}}}{,,,}}
 \item \visible<3->{She \textcolor{Maroon}{\bfseries was playing} tennis two hours ago.{\small 彼女は2時間前テニスをしていた。\\\mbox{}\hfill{}(過去進行形)}}
\visible<4->{\signchart[width=10,height=.5]{{\textcolor{Maroon}{2時間前}},,}{,,,}}
\end{enumerate}



\begin{tikzpicture}[overlay]
 %\draw[gray!50] (0,0) grid (12,5);
 \visible<2->{\draw[ForestGreen!70,line width=6pt,opacity=.5] (9.2,2.95) --(10.6,2.95);}
\visible<4->{ \draw[Maroon!70,line width=6pt,opacity=.7] (4.2,.9) -- (5.6,.9);}
\end{tikzpicture}

\visible<5->{{\small 
\mbox{}\hfill{%
}$\left\{\begin{tabular}[c]{l}
         was\\
         were
       \end{tabular}\right\} + \text{--ing}$
}
}


\vspace{10pt}

\visible<6->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\small
 \item 現在進行形(〜している)$\longrightarrow$今この瞬間に起こっていること
 \item 過去進行形(〜していた)$\longrightarrow$過去のある時点で起こっていること%
\hfill\myaudio{./audio/005_was_ing_intro_01.mp3}

\end{itemize}
     \end{exampleblock}
}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises 1}
1は正しい方を選びましょう。2〜４は日本語の意味になるよう(~~~~~)内の語句を並べ替えましょう。先頭に来る語は大文字で書き始めてください
 \begin{enumerate}
  \item Bob ( is studying / \alt<2->{\Circled[outer color = BurntOrange]{ was studying }}{was studying} ) English last night.
  \item ( is / she / sleeping ) now.彼女はいま眠っています。\\
\visible<3->{She is sleeping now.}
  \item ( I / waiting / was ) for the train then.私はそのとき電車を待っていました。\\
	\visible<4->{I was waiting for the train then.}
  \item ( eating / dinner / was / with  / I  / my family ) at that time.\\
\mbox{}\hfill{}私はそのとき家族と夕飯を食べていました。\\
\visible<5->{I was eating dinner with my family at that time.}
 \end{enumerate}
\hfill\myaudio{./audio/005_was_ing_intro_02.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises 2}
適当な動詞を(~~~~~)内に補い、英文を完成させましょう。必要に応じて適当な形に変えてください

\begin{columns}[t]
\begin{column}{.75\textwidth}
 \begin{enumerate}
  \item He was (~\alt<2->{playing}{\phantom{playing}}~) soccer at that time.
  \item She was  (~\alt<3->{making}{\phantom{making}}~) a delicious dinner for us then.
  \item I was  (~\alt<4->{writing}{\phantom{writing}}~) a letter to my friend at that time.
  \item They were  (~\alt<5->{swimming}{\phantom{swimming}}~) in the pool then.
  \item The dog was  (~\alt<6->{running}{\phantom{running}}~) in the yard at that time. 
 \end{enumerate} 
\end{column} 
\begin{column}{.225\textwidth}
次の中から選んでください
 \begin{tcolorbox}
  swim\\
  run\\
  make\\
  write\\
  play
 \end{tcolorbox}
\end{column}
\end{columns}
\hfill\myaudio{./audio/005_was_ing_intro_03.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{--ingのつくりかた}
 
\begin{center}
% \rowcolors{2}{NavyBlue!50}{yellow!40}
\begin{tblr}{
  colspec = {l l l l}, % 列の仕様
  row{5-6} = {bg=yellow!50}, % 1行目の背景色を黄色に設定
  row{7-8} = {bg=NavyBlue!40} % 3行目の背景色を薄い灰色に設定
}
\toprule
&{\small 原形}&{\small --ing}\\\midrule
1&\visible<1->{eat}&\visible<2->{{\small eating}}&\\
2&\visible<1->{play}&\visible<3->{{\small playing}}&\\
3&\visible<1->{go}&\visible<4->{{\small going}}&\\
4&\visible<1->{make}&\visible<5->{{\small making}}&\visible<5->{eをとって--ing}\\
5&\visible<1->{write}&\visible<6->{{\small writing}}&\\
6&\visible<1->{swim}&\visible<7->{{\small swimming}}&\visible<7->{子音字を重ねて--ing}\\
7&\visible<1->{run}&\visible<8->{{\small running}}&\\
\bottomrule
\end{tblr}%
\end{center}
\hfill\myaudio{./audio/005_was_ing_intro_04.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{過去進行形の否定}
 \begin{enumerate}
  \item \begin{enumerate}
	 \item<1-> Bob was hungry.
	 \item<2-> Bob was \myEmph[2-]{Maroon}{not} hungry.
	\end{enumerate}
  \item \begin{enumerate}
	 \item<3-> Jane \myEmph[3-]{NavyBlue}{was waiting} for the train then.
	 \item<4-> Jane \myEmph[3-]{NavyBlue}{was} \myEmph[4-]{Maroon}{not} \myEmph[3-]{NavyBlue}{waiting} for the train then.
	\end{enumerate}
 \end{enumerate}
\hfill\myaudio{./audio/005_was_ing_intro_05.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{過去進行形の疑問文}
  \begin{enumerate}
  \item \begin{enumerate}
	 \item<1-> Bob was hungry.
	 \item<2-> Was Bob hungry?
	\end{enumerate}
  \item \begin{enumerate}
	 \item<3-> Jane \myEmph[3-]{NavyBlue}{was waiting} for the train then.
	 \item<4-> \myEmph[3-]{NavyBlue}{Was} Jane \myEmph[3-]{NavyBlue}{waiting} for the train then?
	\end{enumerate}

 \end{enumerate}
\hfill\myaudio{./audio/005_was_ing_intro_06.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
 ［~~~~~］内の指示にしたがって英文を書き換えましょう。
さらに3～５は、書き換えた疑問文に対する答えを「はい」と「いいえ」の2とおりつくりましょう\hfill\myaudio{./audio/005_was_ing_intro_07.mp3}

\begin{enumerate}
 \item Bob was playing the violin this morning. ［否定文にする］\\
       \visible<2->{Bob was not playing the violin this morning.}
 \item We were studying science at that time. ［否定文にする］\\
       \visible<3->{We were not studying science at that time.}
 \item He was walking in the park then. ［疑問文にする］\\
       \visible<4->{Was he walking in the park then?}
       \visible<5->{--- Yes, he was. / No, he was not($= \text{wasn't}).$}
 \item She was swimming in the pool. ［疑問文にする］\\
       \visible<6->{Was she seimming in the pool?}
       \visible<7->{--- Yes, she was. / No, she was not($= \text{wasn't}).$}
 \item The cats were sleeping then. ［疑問文にする］\\
       \visible<8->{Were the cats sleeping then?}
       \visible<9->{--- Yes, they were. / No, they were not\makebox[0pt][l]{($= \text{weren't}$).}}

\end{enumerate}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{疑問詞をもちいて}
 \begin{enumerate}
  \item What was she doing at that time? --- She was doing homework.
  \item Where was he running? --- In the park.
	\mbox{}\hfill{}cf. He was running in the park.
  \item Who was watching television? --- John was.
	\mbox{}\hfill{}cf. John was watching television.
 \end{enumerate}

\visible<5->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\small
 \item $\text{疑問詞} + \text{be動詞} + \text{S} + \text{--ing\ldots ?}$
 \item ただし、疑問詞が主語のとき\\
\mbox{}\hspace{40pt}$\text{疑問詞($=$S)} + \text{be動詞} + \text{--ing\ldots ?}$

\end{itemize}
     \end{exampleblock}
}
\hfill\myaudio{./audio/005_was_ing_intro_08.mp3}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
(~~~~~)の語句を並べ替えて対話を完成させましょう。文頭にくる語は大文字で書きはじめてください
\begin{enumerate}
 \item ( doing / you / were/ what ) last night?
--- I was studying history. \\
\visible<2->{What were you doing alast night?}
 \item ( was / what / doing / your brother ) then?
--- He was cleaning his room.\\
\visible<3->{What was your brother doing then?}
 \item ( was / the guitar / playing / who )? --- Paul was.\\
\visible<4->{Who was playing the guitar?}
\end{enumerate}
\hfill\myaudio{./audio/005_was_ing_intro_09.mp3}


\end{frame}
\end{document}
