\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Change alert block colors
%%% 1- Block title (background and text)
\setbeamercolor{block title alerted}{fg=mDarkTeal, bg=mLightBrown!45!yellow!45}
\setbeamercolor{block title example}{fg=magenta!10!black, bg=mLightGreen!70}
%%% 2- Block body (background)
\setbeamercolor{block body alerted}{bg=mLightBrown!25}
\setbeamercolor{block body example}{bg=mLightGreen!15}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
\usepackage{pxrubrica}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{I was watching television when he came.}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}


\begin{frame}[plain]
  \titlepage
\end{frame}


\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}

\section{when \textipa{/w\'en/}}
\subsection{when}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{～するとき}
\Large
 \begin{enumerate}
  \item<1-> I \myAnch{a_1}{white}{\myEmph[2-]{NavyBlue}{was watching}} television \alt<2->{\myAnch{b_1}{Maroon}{then}}{\myAnch{B_1}{white}{then}}.%
\hfill{}\visible<2->{{\scriptsize then \textipa{/D\'en/} そのとき(副詞)}}
  \item<3-> I \myAnch{a_2}{white}{\myEmph[4-]{NavyBlue}{was watching}} television  \alt<4->{\myAnch{b_2}{Maroon}{at that time}}{\myAnch{B_2}{white}{at that time}}.
  \item<5-> I \myAnch{a_3}{white}{\myEmph[6-]{NavyBlue}{was watching}} television   \alt<6->{\myAnch{b_3}{Maroon}{when he came}}{\myAnch{B_3}{white}{when he came}}.
\end{enumerate}
\mbox{}\hfill{\scriptsize \myaudio{./audio/021_when_01.mp3}}
\visible<2->%
{\begin{tikzpicture}[remember picture, overlay]
 \visible<2->{\draw[thick, Maroon, ->] (B_1.north west) to[out=170, in=10] (a_1.north);} 
 \visible<4->{\draw[thick, Maroon, ->] (B_2.north west) to[out=170, in=10] (a_2.north);} 
 \visible<6->{\draw[thick, Maroon, ->] (B_3.north west) to[out=170, in=10] (a_3.north);} 
\end{tikzpicture}}

\begin{block}<7->{Topics for Today}\small
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item   \Circled[fill color = white]{ when s $+$ v }\,は「〜が～するとき」という意味
 \item   \Circled[fill color = white]{ when s $+$ v }\,は全体で「副詞」の役割
\end{itemize}
     \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
日本語の意味になるよう、(~~~~~)内の語句を並べ替えましょう%
\mbox{}\hfill{\scriptsize \myaudio{./audio/021_when_02.mp3}}

\begin{enumerate}
 \item 若いころ母はテニスがうまかった。\\
       My mother was a good tennis player ( was / she / when / young ).\\
       \visible<2->{\textcolor{lightgray}{My mother was a good tennis player} when she was young.}
 \item わたしが見かけたとき、彼は妹といっしょだった。\\
       He was with his sister ( him / saw / when / I ). \\
       \visible<3->{\textcolor{lightgray}{He was with his sister} when I saw him.}
 \item  彼女は14歳のとき、京都にいました。\\
	She ( was / was / Kyoto / she / fourteen / when / in ).\\
       \visible<4->{\textcolor{lightgray}{She} was in Kyoto when she was fourteen.}
\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{\fbox{when S $+$ V}\,の位置}
\begin{frame}[plain]{\fbox{when S $+$ V}\,の位置}
\large
 \begin{enumerate}
  \item \begin{enumerate}
	 \item The door  \myAnch{x_1}{white}{\myEmph[2-]{NavyBlue}{opened}} \alt<2->{\myAnch{y_1}{Maroon}{suddenly}}{\myAnch{Y_1}{white}{suddenly}}.%
	       \hfill{\scriptsize suddenly \textipa{/s\'\textturnv dnli/} とつぜん(副詞)}
	 \item  \alt<3->{\myAnch{y_2}{Maroon}{Suddenly}}{\myAnch{Y_2}{white}{Suddenly}},\,\, the door  \myAnch{x_2}{white}{\myEmph[3-]{NavyBlue}{opened}}.
	\end{enumerate}
  \item \begin{enumerate}
	 \item I \myAnch{x_3}{white}{\myEmph[4-]{NavyBlue}{was reading}} a book \alt<4->{\myAnch{y_3}{Maroon}{at that time}}{\myAnch{Y_3}{white}{at that time}}.
	 \item \alt<5->{\myAnch{y_4}{Maroon}{At that time}}{\myAnch{Y_4}{white}{At that time}},\,\, I \myAnch{x_4}{white}{\myEmph[5-]{NavyBlue}{was reading}} a book.
	\end{enumerate}
  \item \begin{enumerate}
	 \item I \myAnch{x_5}{white}{\myEmph[5-]{NavyBlue}{was sleeping}}
\alt<6->{\myAnch{y_5}{Maroon}{when he came}}{\myAnch{Y_5}{white}{when he came}}.\hfill{}\visible<9->{{\bfseries S $+$ V}\,\,\Circled[fill color = white]{ when s $+$ v }}
	 \item \alt<7->{\myAnch{y_6}{Maroon}{When he came}}{\myAnch{Y_6}{white}{When he came}},\,\, I \myAnch{x_6}{white}{\myEmph[6-]{NavyBlue}{was sleeping}}.\hfill{}\visible<9->{\Circled[fill color = white]{ when s $+$ v }, {\bfseries S $+$ V}}
	\end{enumerate}
 \end{enumerate}

\visible<2->%
{\begin{tikzpicture}[remember picture, overlay]
 \visible<2->{\draw[thick, Maroon, ->] (Y_1.north west) to[out=170, in=10] (x_1.north);} 
 \visible<3->{\draw[thick, Maroon, ->] (Y_2.north east) to[out=5, in=175] (x_2.north);} 
 \visible<4->{\draw[thick, Maroon, ->] (Y_3.north west) to[out=170, in=10] (x_3.north);}
 \visible<5->{\draw[thick, Maroon, ->] (Y_4.north east) to[out=5, in=175] (x_4.north);}  
 \visible<6->{\draw[thick, Maroon, ->] (Y_5.north west) to[out=170, in=10] (x_5.north);}
 \visible<7->{\draw[thick, Maroon, ->] (Y_6.north east) to[out=5, in=175] (x_6.north);}  
\end{tikzpicture}}

\vspace{-20pt}

\begin{block}<8->{Topics for Today}\small
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item   \visible<8->{\Circled[fill color = white]{ when s $+$ v }\,は「〜が～するとき」という意味}%
\mbox{}\hfill{\scriptsize \myaudio{./audio/021_when_03.mp3}}
 \item   \visible<8->{\Circled[fill color = white]{ when s $+$ v }\,は全体で「副詞」の役割}
 \item   \visible<9->{\Circled[fill color = white]{ when s $+$ v }\,は、前にも後ろにも位置します}
	 \begin{enumerate}
	  \item<9-> {\bfseries S $+$ V}\,\,\Circled[fill color = white]{ when s $+$ v }
	  \item<9-> \Circled[fill color = white]{ When s $+$ v }\,,\,\,{\bfseries S $+$ V}
	 \end{enumerate}
\end{itemize}
     \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
つぎの英文を、同じ意味になるようにWhenではじめて書き換えましょう%
\mbox{}\hfill{\scriptsize \myaudio{./audio/021_when_04.mp3}}
\begin{enumerate}
 \item I was five when my brother was born.%
\hfill{}{\scriptsize be born: 生まれる}\\
       $\longrightarrow$\, When \visible<2->{my brother was born, I was five.}
 \item He was with his sister when I saw him.\\
       $\longrightarrow$\, When \visible<3->{I saw him, he was with his sister.}
 \item She was studying when I called her.%
\hfill{}{\scriptsize call: 電話する}\\
       $\longrightarrow$\, When \visible<4->{I called her, she was studying.}
\end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{まとめ}
\begin{frame}[plain]{まとめ}
\begin{block}{Topics for Today}

when \textipa{/w\'en/}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item   \visible{\Circled[fill color = white]{ when s $+$ v }\,は「〜が～するとき」という意味}
 \item   \visible{\Circled[fill color = white]{ when s $+$ v }\,は全体で「副詞」の役割}
 \item   \visible{\Circled[fill color = white]{ when s $+$ v }\,は、前にも後ろにも位置します}
	 \begin{enumerate}
	  \item {\bfseries S $+$ V}\,\,\Circled[fill color = white]{ when s $+$ v }
	  \item \Circled[fill color = white]{ When s $+$ v },\,\,{\bfseries S $+$ V}
.	 \end{enumerate}
\end{itemize}
     \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}<1-2>[plain,label=conjunction]{もうひとつ}
 
\begin{enumerate}
 \item I was sleeping {\bfseries then}
 \item I was sleeping \fcolorbox{black}{yellow!50}{when he came}.%
\hfill{}{\bfseries S $+$ V}\,\,\,\fbox{when s$+$v}
 \item \fcolorbox{black}{yellow!50}{When he came}, I was sleeping.%
\hfill{}\fbox{When s$+$v}\,,\,\,{\bfseries S $+$ V}
\end{enumerate}

\bigskip

\pause
{\bfseries when}という単語は2組の\Circled{主語と動詞の組合せ}をつないでいることになりますね

\hfill{}{\bfseries when}のようなことばを\kenten{接続詞}といいます


\vfill

\pause
\textdbend ところでI was sleepingとhe cameは対等の関係ではありません\\
\hspace{15pt}どちらが文の中心となる主語と動詞だとおもいますか

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain,label=basic]{品詞}
 
\begin{description}
 \item[名詞] 人、動物、植物やモノの名前を表す語\hfill{\small child, cat, flower, desk \ldots}
  \item[代名詞] 名詞の代わりに使う語\hfill{\small I, we, you he, she, it, they, this, that \ldots}
 \item[動詞] 動作や状態を表す語\hfill{\small run, see, speak, eat, study, have, be \ldots{}}
 \item[形容詞] 名詞をくわしく説明する語\hfill{\small big, new, happy, good \ldots}
 \item[副詞] 動詞や形容詞などをくわしく説明する語\hfill{\small quickly, here, then\ldots}
 \item[前置詞] 名詞や代名詞と組み合わせて$+\alpha$の意味をくわえる\\
\hfill{\small in, on, under, with, before, after, from, to \ldots}
 \item<2>[接続詞] {\bfseries when}のように2組の\Circled{主語と動詞の組合せ}を接続する
\end{description}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\againframe<3>[plain]{conjunction}
\end{document}
