\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Change alert block colors
%%% 1- Block title (background and text)
\setbeamercolor{block title alerted}{fg=mDarkTeal, bg=mLightBrown!45!yellow!45}
\setbeamercolor{block title example}{fg=magenta!10!black, bg=mLightGreen!70}
%%% 2- Block body (background)
\setbeamercolor{block body alerted}{bg=mLightBrown!25}
\setbeamercolor{block body example}{bg=mLightGreen!15}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{I know how to make a sandwitch.}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section*{授業の流れ}
%\begin{frame}[plain]
%  \frametitle{授業の流れ}
%  \tableofcontents
%\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{how $+$ to --}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{how to --}
 \begin{enumerate}
  \item<1-> I know it.
  \item<2-> I know the recipe.\hfill{\scriptsize recipe \textipa{/r\'es@pi/} レシピ}
  \item<3-> I know \myAnch{a1}{NavyBlue}{\myEmph[4-]{Maroon}{how to} make a sandwitch}.\hfill{\scriptsize sandwitch \textipa{/s\'\ae nwItS/} サンドイッチ}
 \end{enumerate}
%
\hfill{\tiny 0133}\,{\scriptsize \myaudio{./audio/035_wh_to_do_01.mp3}}
%
\begin{block}<5->{Topics for Today}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \Circled[fill color=white]{ how to 動詞の原形 }\,は、
「どのように～したらいいか」、「～する方法」の意味
 \item  \Circled[fill color=white]{ how to 動詞の原形 }\, の全体が名詞のはたらき
 \end{itemize}
     \end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
日本語の意味になるよう(~~~~~~)内の語句を並べ替えましょう。先頭に来る語は大文字で書き始めてください%
\hfill{\tiny 0140}\,{\scriptsize \myaudio{./audio/035_wh_to_do_02.mp3}}
 \begin{enumerate}
  \item わたしは寿司の作り方を知りません。\\
	( make / I / to / know / sushi / how / don't ) .\\
	\visible<2->{I don't know how to make sushi.}
  \item チェスの遊び方を知っていますか。\\
	( chess / know / play / you / to / do / how ) ?\\
	\visible<3->{Do you know how to play chess?}
  \item この地図には駅への行き方がのっています。\hfill{\scriptsize show: 示す　get to ～: ～へ到着する}\\
	This map ( how / get / shows / to / to ) the station.\\
	\visible<4->{This map shows how to get to the station.}
 \end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%
\section{wh-word $+$ to --}
%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Wh $+$ to --}
\begin{enumerate}
 \item<1->  When she was five, she learned \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{how to} swim}.%
\hfill{\tiny 0303}\,{\scriptsize \myaudio{./audio/035_wh_to_do_03.mp3}}
 \item<2-> I was thinking about \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{when to} start the meeting}.\hfill{\scriptsize think about ～について考える}
 \item<3-> They discussed \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{where to} go next Sunday}.\hfill{\scriptsize discuss \textipa{/dIsk\'\textturnv s/} 議論する}
 \item<4-> He didn't know \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{what to} wear for hot weather}.\hfill{\scriptsize weather \textipa{/w\'eD\textrhookschwa /} 天候}
 \item<5-> I didn't know \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{who to} believe}.\hfill{\scriptsize believe \textipa{/b@l\'i:v/} 信じる}
\item<6-> Tell me \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{which to} choose}.\hfill{\scriptsize tell me: 教えて　choose \textipa{/tS\'u:z/} 選ぶ}
\end{enumerate}

 \begin{block}<7->{Topics for Today}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \Circled[fill color=white]{ 疑問詞 $+$ to 動詞の原形 }\,で、how以外の疑問詞wh-wordも使われます
 \item  \Circled[fill color=white]{ 疑問詞 $+$ to 動詞の原形 }\, の全体が名詞のはたらき
 \end{itemize}
     \end{block}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Wh $+$ to --}
 \begin{tblr}{colspec={ll}}
  \Circled[fill color=white]{ how to $+$ 動詞の原形 }&どのように～したらいいか、～する方法\\
  \Circled[fill color=white]{ when to $+$ 動詞の原形 }&いつ～したらいいか\\
  \Circled[fill color=white]{ where to $+$ 動詞の原形 }&どこで（どこへ）～したらいいか\\
  \Circled[fill color=white]{ what to $+$ 動詞の原形 }&なにを～したらいいか\\
  \Circled[fill color=white]{ who to $+$ 動詞の原形 }&だれを～したらいいか\\
  \Circled[fill color=white]{ which to $+$ 動詞の原形 }&どちらを～したらいいか
   \end{tblr}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
日本語の意味になるよう(~~~~~~)内の単語を並べ替えましょう%
\hfill{\tiny 0232}\,{\scriptsize \myaudio{./audio/035_wh_to_do_04.mp3}}

 \begin{enumerate}
  \item eメールの送り方を知っていますか。\hfill{\scriptsize send \textipa{/s\'end/} 送る}\\%
	Do you know ( send / to / an e-mail / how ) ?\hfill{}
	\visible<2->{\textcolor{BurntOrange}{\bfseries how to send an e-mail}}
  \item いつ彼を訪ねるべきかかんがえています。\\
	I am thinking about ( him / visit / when / to ) .\hfill{}
	\visible<3->{\textcolor{BurntOrange}{\bfseries when to visit him}}
  \item 彼女はどこでチケットを買ったらいいかたずねた。\hfill{\scriptsize buy \textipa{/b\'aI/} 買う}\\
	She asked ( the ticket / where / buy / to  ) .\hfill{}
	\visible<4->{\textcolor{BurntOrange}{\bfseries where to buy the ticket}}\\
  \item 彼女は何を買ったらいいか決めていなかった。\hfill{\scriptsize decide \textipa{/dIs\'aId/} 決める}\\
	She didn't decide (buy / what / to ) .
	\hfill\visible<5->{\textcolor{BurntOrange}{\bfseries what to buy}}
  \item だれをパーティに招待したらいいか、私はわからなかった。\hfill{\scriptsize invite \textipa{/Inv\'aIt/} 招待する}\\
	I didn't know ( invite / to / who ) to the party.\hfill{}
	\visible<6->{\textcolor{BurntOrange}{\bfseries who to invite}}
 \end{enumerate}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%
\section{which 名詞 $+$ to --}
\begin{frame}[plain]{which 名詞 $+$ to --}

\dbend

\bigskip

 \begin{enumerate}
  \item<1-> Tell me \fcolorbox{NavyBlue}{white}{the answer}.\hfill{\scriptsize tell me: 教えて}
  \item<2-> Tell me \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{which to} choose}.\hfill{\scriptsize choose \textipa{/tS\'u:z/} 選ぶ}
  \item<3-> Tell me \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{which} book \textcolor{Maroon}{to} choose}.
  \item<4-> Tell me \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{which} book \textcolor{Maroon}{to} read}.
  \item<5-> Tell me \fcolorbox{NavyBlue}{white}{\textcolor{Maroon}{which} book \textcolor{Maroon}{to} buy}.
 \end{enumerate}
%
\hfill{\tiny 0225}\,{\scriptsize \myaudio{./audio/035_wh_to_do_05.mp3}}
\vfill

\begin{block}<6->{Topic for Today}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \Circled[fill color=white]{ which 名詞 $+$ to 動詞の原形 }\,は、
「どちらの\ldots{}を～したらいいか」の意味
 \end{itemize}
     \end{block}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
