\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{When do you play baseball?}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}[plain]
  \titlepage
\end{frame}

\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{When}
\subsection{When is your birthday?: be動詞のとき}
\begin{frame}[plain]{When is your birthday?} \Large

be動詞のとき

\mbox{}\hspace{55pt}Your birthday is  \alt<3->{\myAnch{FOCUS}{orange}{August 7th}}{\myAnch{focus}{white}{August 7th}}.

\pause


\vspace{7pt}

\mbox{}\hfill{}cf. \myEmph[6-]{Maroon}{Is your birthday} August 7th?%

\vspace{-5pt}

\hfill{\small YesまたはNoで答える疑問文}

\pause

\visible<4->{\myAnch{wh}{orange}{When} \myEmph[6-]{Maroon}{is your birthday} \myAnch{question}{orange}{?}}
\visible<6->{\scalebox{1.4}{\myDownwardPitch}}

\pause

%\mbox{}\hspace{30pt}\myAnch{txt1}{white}{\small 先頭にWho}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
\draw[->, thick, orange] (focus.south) to[out=-90, in=90] (wh.north);
\end{tikzpicture}
}
\vspace{-10pt}

\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item 疑問詞{\bfseries when}（いつ？）\,\,\textipa{/w\'en/}
 \item When is 〜?\,\,$\longrightarrow$「〜はいつ」と聞くとき
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）\mbox{}\hfill\myaudio{./audio/014_when_01.mp3}
\end{itemize}
     \end{exampleblock}
}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{When do you play tennis?: 一般動詞のとき}
\begin{frame}[plain]\frametitle{When do you play tennis?}
\Large
一般動詞のとき

\pause

\mbox{}\hspace{55pt}%
You play tennis \alt<4->{\myAnch{FOCUS2}{orange}{on Sundays}}{\myAnch{focus2}{white}{on Sundays}}.

\pause

\mbox{}\hfill%
{\small cf. \myEmph[6-]{Maroon}{Do you play} tennis on Sundays?}

\vspace{-5pt}

\hfill\visible<3->{{\small Yes/Noで答える疑問文}}

\visible<5->{\myAnch{WH2}{orange}{When} \myEmph[6-]{Maroon}{do you play} tennis\myAnch{question2}{orange}{?}}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
 \draw[thick, orange, ->] (focus2.south) to[out=-90, in=90] (WH2.north);
\end{tikzpicture}
}

\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item `When'を先頭に置いて、疑問文のかたちを続ける\,\,When do you  〜?
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}

\mbox{}\hfill\myaudio{./audio/014_when_02.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%


\subsection{Exercises}
\begin{frame}[plain]{Exercises 1}
つぎの文の意味を考えましょう

\begin{tabular}{rll}
1& When is the concert? &　　{\small concert: コンサート} \\
2& When is the party?& \\
3& When do you get up? & {\small get up: 起きる}\\
4& When does the meeting begin?&　　{\small meeting: 会議　begin: 始まる} \\
\end{tabular}


\mbox{}\hfill\myaudio{./audio/014_when_03.mp3}

\end{frame}

\begin{frame}[plain]{Exercises 2}
 次の質問に対する答えとしてもっとも適切なものを，下のア～ウの中から選びましょう

\begin{enumerate}
 \item When do you usually\footnote{いつも} practice\footnote{練習する} basketball?\hspace{10pt}\visible<2->{--- On Saturdays.}\hspace{21pt}\visible<3->{イ}
 \item When is St. Valentine's Day\footnote{バレンタインデー}?\hspace{80pt}\visible<4->{--- It's February 14th.}\hspace{12pt}\visible<5->{ウ}
 \item When does the school year start in Japan?\hspace{15pt}\visible<6->{--- In April.}\hspace{50pt}\visible<7->{ア}
\end{enumerate}

\begin{tcolorbox}
\centering
ア In April.~~~~~~~~%
イ On Saturdays.~~~~~~~~%
ウ It's February 14th. 
\end{tcolorbox}

%
\mbox{}\hfill\myaudio{./audio/014_when_04.mp3}


\end{frame}


\begin{frame}[plain]{Exercises 3}
 (~~~~~~~~) 内の語句を並べかえ、AとBの対話を完成させましょう。なお、先頭の語は大文字で始めてください

\begin{enumerate}
 \item A: ( Children's Day / when / is ) ? 
\hspace{137.4pt}B: It's May 5th.\\
\phantom{A: }\visible<2->{When is Children's Day?}
 \item A: ( birthday / your / father's / when / is ) ?
\hspace{83.5pt}B: It's July 2nd.\\
\phantom{A: }\visible<3->{When is your father's birthday?}
 \item A: ( to school / does / Mr. Brown / come / when ) ?
\hspace{47pt}B: Around 7:00.\\
\phantom{A: }\visible<4->{When does Mr. Brown come to school?}
 \item A: ( does / the violin / when / play / your brother ) ?
\hspace{39.7pt}B: After dinner.\\
\phantom{A: }\visible<5->{When does your brother play the violin?}
\end{enumerate}

\mbox{}\hfill\myaudio{./audio/014_when_05.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{まとめ}
 \begin{block}{When ～?}
\begin{description}[　　　　]
 \item[be動詞] When is ～?
 \item[一般動詞] When do you ～? / When does he ～?
\end{description}
  
 \end{block}
\end{frame}
\end{document}
