\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{Where does Jane live?}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}[plain]
  \titlepage
\end{frame}

\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}


\section{where \textipa{/w\'e\textrhookschwa /}}

\subsection{Where is your key?: be動詞のとき}
\begin{frame}[plain]{Where is your key?}
 \Large

be動詞のとき

\mbox{}\hspace{10pt}Your key is  \alt<4->{\myAnch{FOCUS}{orange}{on the desk}}{\myAnch{focus}{white}{on the desk}}.
\pause
\hfill{}cf. \myEmph[6-]{Maroon}{Is your key} on the desk?\pause%

\hfill{\normalsize Yes/Noで答える疑問文}

\vspace{7pt}

\pause

\visible<5->{\myAnch{wh}{orange}{Where} \myEmph[6-]{Maroon}{is your key} \myAnch{question}{orange}{?}}
\visible<7->{\scalebox{1.4}{\myDownwardPitch}}

\pause

%\mbox{}\hspace{30pt}\myAnch{txt1}{white}{\small 先頭にWho}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
\draw[->, thick, orange] (focus.south) to[out=-90, in=90] (wh.north);
\end{tikzpicture}
}

\visible<8->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item 「どこ」と聞くときは{\bfseries where}を先頭に
 \item {\bfseries Where}に続く部分は疑問文の語順
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}
\mbox{}\hfill\myaudio{./audio/015_where_01.mp3}

\end{frame}

\subsection{Where do they live?: 一般動詞のとき}
\begin{frame}[plain]\frametitle{Where do they live?}
\Large
一般動詞のとき

They live \alt<4->{\myAnch{FOCUS2}{orange}{in Sydney}}{\myAnch{focus2}{white}{in Sydney}}.
\pause
\hfill{}%
cf. \myEmph[6-]{Maroon}{Do they live} in Sydney?\pause

\hfill{\normalsize Yes/Noで答える疑問文}

\visible<5->{\myAnch{WH2}{orange}{Where}  \myEmph[6-]{Maroon}{do they live}\myAnch{question}{orange}{?}}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
 \draw[thick, orange, ->] (focus2.south) to[out=-165, in=15] (WH2.north east);
\end{tikzpicture}
}

\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item 「どこ」と聞くときは{\bfseries where}を先頭に
 \item {\bfseries Where}に続く部分は疑問文の語順
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}
\mbox{}\hfill\myaudio{./audio/015_where_02.mp3}

\end{frame}

\subsection{Exercises}
\begin{frame}[plain]{Exercises}
つぎの文の意味を考えましょう。

\begin{tabular}{rll}
1& Where is my phone? &　　{\small phone: 電話} \\
2& Where are your shoes?& 　　{\small shoe:くつ}\\
3& Where do they go for vacation? & 　　{\small vacation: バケーション}\\
4& Where does the cat sleep?&　　{\small sleep: 眠る} \\
\end{tabular}

\mbox{}\hfill\myaudio{./audio/015_where_03.mp3}

\end{frame}

\begin{frame}[plain]{Exercises}
 次の質問に対する答えとしてもっとも適切なものを、右のア～オの中から選びましょう。

\begin{columns}[t]
 \begin{column}{.475\textwidth}
\begin{enumerate}
 \item A: Where is Mr. Brown from?\\
B: \alt<2->{He's from the USA. ウ}{(\hspace{100pt})}
 \item A: Where does Naomi live?\\
B: \alt<3->{She lives in Narita. ア}{(\hspace{100pt})}
 \item A: Where does this bus go?\\
B: \alt<4->{It goes to Chiba Station. エ}{(\hspace{100pt})}
 \item A: Where does Tom study?\\
B: \alt<5->{He studies in the library. イ}{(\hspace{100pt})}
 \item A: Where is Mary now?\\
B: \alt<6->{She's in the kitchen now. オ}{(\hspace{100pt})}
\end{enumerate}  
 \end{column}
\begin{column}{.475\textwidth}
\begin{tcolorbox}
ア She lives in Narita.\\
イ He studies in the library.\\
ウ He's from the USA.\\
エ It goes to Chiba Station.\\
オ She's in the kitchen now.
\end{tcolorbox} 
\mbox{}\hfill\myaudio{./audio/015_where_04.mp3}
\end{column}
\end{columns}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
