\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{Which is your favorite color?}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}[plain]
  \titlepage
\end{frame}


\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}



\section{Which}

\subsection{Which is your favorite season?: be動詞のとき}
\begin{frame}[plain]{Which is your favorite season?}
 \Large

be動詞のとき

Your favorite season is \alt<4->{\myAnch{FOCUS}{orange}{spring}}{\myAnch{focus}{white}{spring}}.\hfill{\small favorite: お気に入りの}
\pause


\hfill{}\myEmph[6-]{Maroon}{Is your favorite season} spring?\pause%

\hfill{\normalsize YesまたはNoで答える疑問文}

\vspace{7pt}

\pause

\visible<5->{\myAnch{wh}{orange}{Which} \myEmph[6-]{Maroon}{is your favorite season} \myAnch{question}{orange}{?}}
\visible<6->{\scalebox{1.4}{\myDownwardPitch}}

\pause


\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
\draw[->, thick, orange] (focus.south) to[out=-90, in=90] (wh.north);
\end{tikzpicture}
}

\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\small
 \item 「どれ、どちら」と聞くとき$\longrightarrow$\,\,\,which is 〜 ?
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}
\visible<8->{%
\mbox{}\hfill\myaudio{./audio/015_which_01.mp3}
}
\end{frame}

\begin{frame}[plain]\frametitle{Which is your favorite color, pink or blue?}
\Large
 
\begin{enumerate}
\visible<1->{ \item Which is your favorite season?} \hfill\visible<2->{{\small (四季のうち)どれ}}
\visible<3->{ \item \textcolor{orange}{\bfseries Which} is your favorite color, \colorbox{pink}{pink}  \textcolor{orange}{\bfseries or} \colorbox{blue!50}{blue} ?}\hfill\visible<4->{{\small AとBのどちら}}
\end{enumerate}

\vspace{20pt}

\visible<5->{%
\begin{exampleblock}{Topic for Today}
\pause
\begin{itemize}
 \item 「AとBのどちら」と聞くとき$\longrightarrow$\,\,\,\textcolor{orange}{\bfseries Which}  is 〜, \textcolor{orange}{\bfseries A or B} ?
\end{itemize}
     \end{exampleblock}
}
\visible<6->{%
\mbox{}\hfill\myaudio{./audio/015_which_02.mp3}
}
\end{frame}

\begin{frame}[plain]{Exercises}
つぎの文の意味を考えましょう。

\begin{enumerate}
 \item Which is Ken's bag?
 \item Which is your pencil?
 \item Which is your favorite drink, tea or coffee?

\end{enumerate} 

\pause

\mbox{}\hfill\myaudio{./audio/015_which_03.mp3}
\end{frame}


\subsection{Which do you like?: 一般動詞のとき}
\begin{frame}[plain]\frametitle{Which season do you like?}
\Large
一般動詞のとき

\pause

\mbox{}\hspace{60pt}You like  \alt<5->{\myAnch{FOCUS2}{orange}{summer}}{\myAnch{focus2}{white}{summer}}.\pause

\mbox{}\hfill%
\myEmph[6-]{Maroon}{Do you like} summer?

\vspace{-5pt}

\mbox{}\hfill{}\visible<4->{{\small Yes/Noで答える疑問文}}

\visible<6->{\myAnch{WH2}{orange}{Which} \myEmph[6-]{Maroon}{do you like}, spring \textcolor{orange}{\bfseries or} summer?}\hfill\visible<7->{{\small AとBのどちら}}

\visible<8->{%
\begin{tikzpicture}[remember picture, overlay]
 \draw[thick, orange, ->] (focus2.south) to[out=-90, in=90] (WH2.north);
\end{tikzpicture}
}

\visible<9->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\small
 \item `Which'を先頭に置いて、疑問文のかたちを続ける\,\,Which do you  〜?
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}
\visible<10->{%
\mbox{}\hfill\myaudio{./audio/015_which_04.mp3}
}
\end{frame}

\subsection{Exercises}
\begin{frame}[plain]{Exercises}
つぎの文の意味を考えましょう。

\begin{tabular}{rll}
1& Which does he need, a pen or a pencil? &　　{\small need: 必要とする} \\
2&Which does she eat for breakfast, cereal or toast? & 　　{\small cereal: シリアル}\\
3& Which do you like, Englsi or math? & 　　{\small math: 数学}\\
4& Which do they speak, English or Spanish?&　　{\small Spanish: スペイン語} \\
\end{tabular}

\visible<2->{%
\mbox{}\hfill\myaudio{./audio/016_which_05.mp3}
}
\end{frame}


\begin{frame}[plain]{Exercises}
 あたえられた状況に合うように、(~~~~~~~) に適語を入れなさい。

\begin{enumerate}
 \item どれが相手の自転車かをたずねる場合\\
\alt<2->{\textcolor{orange}{Which}}{(\hspace{30pt})} is your bike?
 \item ピザとパスタのどちらが好きかをたずねる場合\\
\alt<3->{\textcolor{orange}{Which}}{(\hspace{30pt})} do you like, pizza \alt<3->{\textcolor{orange}{or}}{(\hspace{30pt})} pasta?
 \item 猫と犬のどちらを飼いたいかをたずねる場合\\
\alt<4->{\textcolor{orange}{Which}}{(\hspace{30pt})} do you want, a cat \alt<4->{\textcolor{orange}{or}}{(\hspace{30pt})} a dog?
\end{enumerate}

\visible<5->{%
\mbox{}\hfill\myaudio{./audio/016_which_06.mp3}
}
\end{frame}

\begin{frame}[plain]{$\text{Which} + \text{名詞}$}
\begin{enumerate}
 \visible<1->{\item \myAnch{pron}{orange}{Which} do you like, tea or coffee?}
 \visible<2->{\item \myAnch{adj}{orange}{which\raisebox{5pt}{$\curvearrowright$}drink} do you like, tea or coffee?\\ {\small どちらの飲みもの}}
\end{enumerate}

\visible<3->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\small
 \item \fbox{$\text{Which} + \text{名詞}$}\,\,がひとかたまりになって「どちらの〜」の意味で使うことがあります
 \item \fbox{$\text{Which} + \text{名詞}$}\,\,も文の先頭にきます
\end{itemize}
     \end{exampleblock}
}
\visible<4->{%
\mbox{}\hfill\myaudio{./audio/015_which_07.mp3}
}
\end{frame}


\begin{frame}[plain]{Exercises}
つぎの文の意味を考えましょう。

\begin{enumerate}
 \item \visible<1->{Which color do you like, red or blue?}\hfill\visible<2->{color: 色}
 \item \visible<1->{Which subject  do you like, music or art?}\hfill\visible<3->{subject: 科目}
 \item \visible<1->{Which language do they speak, English or French?}\hfill\visible<4->{language: 言語}
 \item \visible<1->{Which animal does she have, a cat or a dog?}\hfill\visible<5->{animal: 動物}
\end{enumerate} 

\visible<6->{%
\mbox{}\hfill\myaudio{./audio/015_which_08.mp3}
}
\end{frame}

\end{document}
