\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{How are you?}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}[plain]
  \titlepage
\end{frame}

\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How（単独）}
\subsection{How are you?: be動詞のとき}
\begin{frame}[plain]{How is 〜?}
\large

be動詞のとき

\mbox{}\hspace{50pt}Your father is  \alt<3->{\myAnch{FOCUS}{orange}{fine}}{\myAnch{focus}{white}{fine}}.

\pause


\vspace{7pt}

\mbox{}\hfill{}cf. \myEmph[6-]{Maroon}{Is your father} fine?%

\vspace{-5pt}

\hfill{\small YesまたはNoで答える疑問文}

\pause

\visible<4->{\myAnch{wh}{orange}{How} \myEmph[6-]{Maroon}{is your father} \myAnch{question}{orange}{?}}
\visible<6->{\scalebox{1.4}{\myDownwardPitch}}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
\draw[->, line width=3pt,opacity=.5, orange] (focus.south) to[out=-90, in=90] (wh.north);
\end{tikzpicture}
}
\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item 「〜はどうですか」と聞くとき
（Howの後ろは疑問文の語順）\\
$\longrightarrow$\,\,\,How is 〜?
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}
\vspace{-10pt}
\hfill\myaudio{./audio/017_how_01.mp3}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{How are 〜?}
\large

be動詞のとき

\mbox{}\hspace{46pt}Your parents are  \alt<3->{\myAnch{FOCUS_2}{orange}{fine}}{\myAnch{focus_2}{white}{fine}}.

\pause


\vspace{7pt}

\mbox{}\hfill{}cf. \myEmph[6-]{Maroon}{Are your parents} fine?%

\vspace{-5pt}

\hfill{\small YesまたはNoで答える疑問文}

\pause

\visible<4->{\myAnch{wh_2}{orange}{How} \myEmph[6-]{Maroon}{are your parents} \myAnch{question}{orange}{?}}
\visible<6->{\scalebox{1.4}{\myDownwardPitch}}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
\draw[->, line width=3pt,opacity=.5, orange] (focus_2.south) to[out=-90, in=90] (wh_2.north);
\end{tikzpicture}
}
\visible<7->{%
\begin{exampleblock}{Topics for Today}\small
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item 「〜はどうですか」と聞くとき
（Howの後ろは疑問文の語順）\\
$\longrightarrow$\,\,\,How is 〜? / How are 〜?
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\hfill\myaudio{./audio/-17_how_02.mp3}%
\end{itemize}
     \end{exampleblock}
}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises 1}
 日本語の意味になるように、語句を並べ替えましょう。先頭にくる語は大文字で書き始めてください
\begin{enumerate}
 \item ( is / mother / how / your )
あなたのお母さんはいかがですか？\\
\visible<2->{How is your mother?}\\
\visible<3->{--- She is very well, thank you.おかげさまでとても元気です}\\
 \item  ( how / you / are )お元気ですか？\\ 
\visible<4->{How are you?}
\visible<5->{--- Good.元気ですよ}\\
 \item ( is / in / how / the weather / Boston )
ボストンの天気はどうですか？\\
\visible<6->{How is the weather in Boston?}
\visible<7->{---\begin{tabular}[t]{l@{\,\,\,}ll}
	      It's& sunny. &(晴れ) \\
                  & \visible<8->{cloudy.}&\visible<8->{(曇り)}\\
                  & \visible<9->{rainy.}&\visible<9->{(雨)}\\
                  & \visible<10->{snowy.}&\visible<10->{(雪)}
	     \end{tabular}}
\end{enumerate}
\hfill{\scriptsize \myaudio{./audio/017_how_03.mp3}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{How does she go to work?: 一般動詞のとき}
\begin{frame}[plain]\frametitle{How does she go to work?}
\large
一般動詞のとき

\pause

\mbox{}\hspace{55pt}%
She goes to work \alt<4->{\myAnch{FOCUS_3}{orange}{by bus}}{\myAnch{focus_3}{white}{by bus}}.

\pause

\mbox{}\hfill%
{\small cf. \myEmph[6-]{Maroon}{Does she go} to work by bus?}

\vspace{-5pt}

\hfill\visible<3->{{\small Yes/Noで答える疑問文}}

\visible<5->{\myAnch{WH_3}{orange}{How} \myEmph[6-]{Maroon}{does she go} to work\myAnch{question2}{orange}{?}}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
 \draw[ line width=3pt,opacity=.5,orange, ->] (focus_3.south) to[out=-90, in=90] (WH_3.north);
\end{tikzpicture}
}

\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item `How'を先頭に置いて、疑問文のかたちを続ける\,\,How do you  〜? / How does she 〜? 
 \item   文末に`?'をつける（イントネーションは\myDownwardPitch{}\,\,）
\end{itemize}
     \end{exampleblock}
}
\vspace{-10pt}
\hfill\myaudio{./audio/017_how_04.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises 2}
 日本語の意味になるように、空所に適当な語を補いましょう
\begin{enumerate}
 \item その映画について，あなたはどう感じていますか\\
       (~~\alt<4->{How}{\phantom{How}}~~)  (~~\alt<4->{do}{\phantom{do}}~~)  you feel about the movie? --- It is great.
 \item 冬休みはどうやってすごしますか --- いつも祖母のところに行きます\\
       (~~\alt<5->{How}{\phantom{How}}~~)  (~~\alt<5->{do}{\phantom{do}}~~)  you spend the winter vcation?\\
 --- I usually visit my grandmother. \item 彼はどうやって公園に行きますか --- 歩いて行きます\\
       (~~\alt<6->{How}{\phantom{How}}~~)  (~~\alt<6->{does}{\phantom{does}}~~)  he go to the park? --- He goes there on  (~~\alt<7->{foot}{\phantom{foot}}~~) .
\end{enumerate}

\mbox{}\hfill\visible<8->{{\scriptsize on foot: 徒歩で}}

\hfill\myaudio{./audio/017_how_05.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{\fbox{How $+$ X} どれくらい、どれほど}
\begin{frame}[plain]{How old 〜?}
 \begin{enumerate}
  \item \myEmph[2-]{Maroon}{How old} is the building? --- It is 80 years old.%
\hfill{}\visible<2->{{\small \fbox{How\raisebox{5pt}{$\curvearrowright$}old}}}
  \item \myEmph[3-]{Maroon}{How tall }is the tower? --- It is fifty meters.%
\hfill{}\visible<3->{\small {\fbox{How\raisebox{5pt}{$\curvearrowright$}tall}}}
  \item \myEmph[4-]{Maroon}{How long} is the bridge? --- It is 100 meters.
\hfill{}\visible<4->{\small {\fbox{How\raisebox{5pt}{$\curvearrowright$}long}}}
  \item \myEmph[5-]{Maroon}{How many} dogs do you have? --- I have two.
\hfill{}\visible<5->{\small {\fbox{How\raisebox{5pt}{$\curvearrowright$}many\raisebox{5pt}{$\curvearrowright$}dogs}}}
  \item \myEmph[6-]{Maroon}{How much} is the book? --- It is 10 dollars.
\hfill{}\visible<6->{\small {\fbox{How\raisebox{5pt}{$\curvearrowright$}much}}}
 \end{enumerate}

\visible<7->{%
\begin{exampleblock}{Topics for Today}
\pause
\begin{itemize}\small
 \item 「どのくらい」と`程度'をたずねるとき$\longrightarrow$\,\,\,$\text{How} + \text{形容詞}$\,\ldots{}?
 \item   「いくら」と`値段'をたずねるとき$\longrightarrow$\,\,\,$\text{How much}$\,\ldots{}?
\end{itemize}
     \end{exampleblock}
}

\hfill\myaudio{./audio/017_how_06.mp3}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{How ...?}
 
 \begin{center}
 \rowcolors{1}{NavyBlue!50}{yellow!40}
\begin{tabular}{ll}\toprule
年齢や古さ& How old \ldots{}\, ?\\
身長や高さ& How tall \ldots{}\, ?\\
長さ&How long \ldots{}\, ?\\
数&How many 名詞 \ldots{}\, ?\\
値段&How much \ldots{}\, ?\\
\bottomrule
\end{tabular}
\end{center}
\end{frame}
%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises 3}
 
 次の対話の ( ) に入れるのにもっとも適切なものをア～オからそれぞれ1つずつ選び
ましょう
\begin{columns}
\begin{column}{.65\textwidth}
\begin{enumerate}
 \item A: How many brothers do you have?\\
B: \alt<2->{( Two brothers. ) イ}{( \phantom{Two brothers.} )}
\item A: How much is the notebook? \\
B:  \alt<3->{( 100 yen. ) エ}{(\phantom{ 100 yen. })} 
 \item  A: How many hours do you study every night?\\ 
B:  \alt<4->{( About two hours. ) ウ}{(\phantom{ About two hours. })} 
  \item A: How old is your brother?\\
B:  \alt<5->{( Fifteen years old. ) ア}{(\phantom{Fifteen years old. })}
\end{enumerate} 
\end{column}
\begin{column}{.35\textwidth}
\begin{tcolorbox}
 
ア Fifteen years old.\\
イ Two brothers.\\
ウ About two hours.\\
エ 100 yen.
\end{tcolorbox}
\hfill\myaudio{./audio/017_how_07.mp3}


\end{column}
\end{columns}

\end{frame}
\end{document}

