\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{What is this?}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\begin{frame}[plain]
  \titlepage
\end{frame}

\section*{授業の流れ}
\begin{frame}[plain]
  \frametitle{授業の流れ}
  \tableofcontents
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{What \textipa{/w\'At/}}
\subsection{be動詞のとき}
\begin{frame}[plain]{be動詞のとき}

\Large
\mbox{}\hspace{55pt}This is \alt<3->{\myAnch{FOCUS}{orange}{a laptop}}{\myAnch{focus}{white}{a laptop}}.\hfill{\scriptsize laptop \textipa{/l\'\ae ptAp/} ノートパソコン}

\pause


\vspace{7pt}

\mbox{}\hfill{}cf. \myEmph[6-]{Maroon}{Is this} a laptop?%

\vspace{-5pt}

\hfill{\small YesまたはNoで答える疑問文}

\pause

\visible<4->{\myAnch{wh}{orange}{What} \myEmph[6-]{Maroon}{is this} \myAnch{question}{orange}{?}}
\visible<6->{\scalebox{1.4}{\myDownwardPitch}}



\pause

%\mbox{}\hspace{30pt}\myAnch{txt1}{white}{\small 先頭にWho}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
\draw[->, line width=3pt, opacity=.5, orange] (focus.south) to[out=-90, in=90] node[sloped,above,text=black,font=\tiny,pos=.5]{whatに置き換えて先頭へ} node[sloped,below,text=black,font=\tiny,pos=.5]{後は疑問文の語順} (wh.north);
\end{tikzpicture}
}

\begin{block}<7->{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \<「何」とたずねるときは疑問詞\textbf{what}をつかいます\hfill{\scriptsize \textbf{What} is your name?}
 \item \textbf{What}は文の先頭に / 後は疑問文の語順
 \item   文末に`?'をつける / イントネーションは\myDownwardPitch{}
\end{itemize}
     \end{block}


\vspace{-10pt}
\visible<1->{%
\mbox{}\hfill{\tiny 0132}\,{\scriptsize \myaudio{./audio/019_what_01.mp3}}
}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{一般動詞のとき}
\begin{frame}[plain]\frametitle{一般動詞のとき}
\Large

\pause

\mbox{}\hspace{55pt}%
You want \alt<4->{\myAnch{FOCUS2}{orange}{pizza}}{\myAnch{focus2}{white}{pizza }} for dinner.

\pause

\mbox{}\hfill%
{\small cf. \myEmph[6-]{Maroon}{Do you want} pizza for dinner?}

\vspace{-5pt}

\hfill\visible<3->{{\small Yes/Noで答える疑問文}}

\visible<5->{\myAnch{WH2}{orange}{What} \myEmph[6-]{Maroon}{do you want} for dinner\myAnch{question2}{orange}{?}}

\visible<5->{%
\begin{tikzpicture}[remember picture, overlay]
 \draw[line width=3pt, opacity=.5, orange, ->] (focus2.south) to[out=-90, in=90] node[sloped,above,text=black,font=\tiny,pos=.5]{whatに置き換えて先頭へ} node[sloped,below,text=black,font=\tiny,pos=.5]{後は疑問文の語順} (WH2.north);
\end{tikzpicture}
}

\begin{block}<7->{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \<「何を」とたずねるときは疑問詞\textbf{what}をつかいます\hfill{\scriptsize \textbf{What} do you eat for breakfast?}
 \item \textbf{What}は文の先頭に / 後は疑問文の語順
 \item   文末に`?'をつける / イントネーションは\myDownwardPitch{}
\end{itemize}
     \end{block}

\mbox{}\hfill{\tiny 0134}\,{\scriptsize \myaudio{./audio/019_what_02.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
 

(~~~~~) 内の語句を並べかえ、対話を完成させましょう。なお、先頭に来る語は大文字ではじめてください
\begin{enumerate}
 \item ( his name / is / what ) ? --- His name is John.\\
\visible<2->{What is his name?}
 \item ( favorite sport / is / what / your ) ? --- I love baseball.\\
\visible<3->{{What is your favorite sport?}}\hfill{\scriptsize favorite \textipa{/f\'eIv@r@t/} おきにいりの}
 \item ( morning / you / drink / do / what / every ) ? --- I drink milk.\\
\visible<4->{What do  you drink every morning?}
 \item ( does / study / what / she ) every day? --- She studies English.\\
\visible<5->{What does she study every day?}\end{enumerate}

\mbox{}\hfill{\tiny 0253}\,{\scriptsize \myaudio{./audio/019_what_03.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{what $+$ 名詞}
\begin{frame}[plain]{$\text{What} + \text{名詞}$}
\begin{enumerate}
 \visible<1->{\item \myAnch{adj}{orange}{What\raisebox{5pt}{$\curvearrowright$}time} is it? --- It is ten forty.%\hfill{}{\small cf. It is ten forty.}\\
\\ {\small 何時}}
 \visible<2->{\item \myAnch{adj}{orange}{What\raisebox{5pt}{$\curvearrowright$}sport} do you like? --- I like baseball.\\ {\small 何のスポーツ}}
\end{enumerate}

\begin{block}<3->{Topics for Today}
\pause
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \fcolorbox{black}{white}{$\text{What} + \text{名詞}$}\,\,がセットになって「何の〜、どんな～」の意味で使うことがあります
 \item \fcolorbox{black}{white}{$\text{What} + \text{名詞}$}\,\,も文の先頭にきます / 後は疑問文の語順
\end{itemize}
     \end{block}

\mbox{}\hfill{\tiny 0134}\,{\scriptsize \myaudio{./audio/019_what_04.mp3}}



\end{frame}
%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
 対話になるように(~~~~~~)内の語句を並べ替えましょう。先頭にくる語は
大文字ではじめてください\hfill{\tiny 0322}\,{\scriptsize \myaudio{./audio/019_what_05.mp3}}

\begin{enumerate}
 \item ( watch / what / you / movies / do ) ? --- I watch action movies.\\
\visible<2->{What movies do you watch?}
 \item ( books / you / read / what / do ) ? --- I read mystery novels.\\
\visible<3->{What books do you read?}\hfill{\scriptsize novel \textipa{/n\'Avl/} 小説}
 \item ( hobbies / you / have / do / what ) ?\hfill{}{\scriptsize hobby \textipa{/h\'Abi/} 趣味}\\
\mbox{}\hspace{20pt}--- I have hobbies like painting and reading.\hfill{}{\scriptsize like 〜のような}\\
\visible<4->{What hobbies do you have?}
 \item ( is / day / what / it )  today? --- It's Saturday.\\
\visible<5->{What day is it today?}\hfill{}\visible<6->{{\small \textdbend\,What day \textbf{of the week} is it today?}}
\end{enumerate}


\end{frame}
%%%%%%%%%%%%%%%%%%%
\section{まとめ}
\begin{frame}[plain]{疑問詞whatのまとめ}

\begin{block}{疑問詞what \textipa{/w\'At/}}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \<「何」とたずねるときは疑問詞\textbf{what}をつかいます%
\hfill{\scriptsize \textbf{What} is your favorite sport?}\\
\hfill{\scriptsize \textbf{What} do you eat for breakfast?}
 \item \textbf{What}は文の先頭に / 後は疑問文の語順
 \item   文末に`?'をつける / イントネーションは\myDownwardPitch{}
\end{itemize}
     \end{block}

\begin{block}{Topics for Today}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \fcolorbox{black}{white}{$\text{What} + \text{名詞}$}\,\,がセットになって「何の〜、どんな～」の意味で使うことがあります
 \item \fcolorbox{black}{white}{$\text{What} + \text{名詞}$}\,\,も文の先頭にきます / 後は疑問文の語順\\
\hfill{\scriptsize \textbf{What} books do you like?}\\
\hfill{\scriptsize \textbf{What} day is it today? / \textbf{What} day \textbf{of the week} is it today?}
\end{itemize}
     \end{block}

\hfill{\tiny 0213}\,{\scriptsize \myaudio{./audio/019_what_06.mp3}}
\end{frame}
\end{document}
