\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Change alert block colors
%%% 1- Block title (background and text)
\setbeamercolor{block title alerted}{fg=mDarkTeal, bg=mLightBrown!45!yellow!45}
\setbeamercolor{block title example}{fg=magenta!10!black, bg=mLightGreen!60}
%%% 2- Block body (background)
\setbeamercolor{block body alerted}{bg=mLightBrown!25}
\setbeamercolor{block body example}{bg=mLightGreen!15}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
\usepackage{pxrubrica}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{いつだれがどこでなにをどんなふうにどうして?}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

%\section*{授業の流れ}
%\begin{frame}[plain]
%  \frametitle{授業の流れ}
%  \tableofcontents
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}<1-3>[plain]{疑問詞の一覧表}
 

\begin{tblr}{
  width = { 1\linewidth },
  hline{1,Z} = { 0.08em },
  hline{2} = { 0.05em },
  colspec = { X[1,l]X[2,l]X[1,l]X[4,l] },
  row{odd} = { gray9 },
  row{1} = { halign = c, bg = gray6, fg = white},
}
 疑問詞&意味&発音&例文\\
who&だれ&\textipa{/h\'u:/}&Who teaches music?\\
whose&だれの&\textipa{/h\'u:z/}&Whose songs \alt<1-2>{do}{\textbf{do}} you like?\\
how&どのように\par{}どれくらい&\textipa{/h\'aU/}&How \alt<1-2>{does}{\textbf{does}} she go to work?\par{}\visible<1>{How long is the river?}\\
when&いつ&\textipa{/w\'en/}&When \alt<1-2>{does}{\textbf{does}} the meeting begin?\\
where&どこで&\textipa{/w\'e\textrhookschwa /}&Where \alt<1-2>{do}{\textbf{do}} they live?\\
why&なぜ&\textipa{/w\'aI/}&Why \alt<1-2>{do}{\textbf{do}} you like jazz?\\
what&なに&\textipa{/w\'At/}&What \alt<1-2>{do}{\textbf{do}} you drink every morning?\\
which&どちら、どれ&\textipa{/w\'ItS/}&Which \alt<1-2>{do}{\textbf{do}} you like, pizza or pasta?\\
\end{tblr}

\hfill{\scriptsize \myaudio{./audio/020a_wh_01.mp3}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\setbeamercolor{background canvas}{bg=black}
\begin{frame}[plain]{\dbend\,\,\,doがあったりなかったり}
\centering
 \scalebox{16}{\textcolor{white}{?}}
\end{frame}
\setbeamercolor{background canvas}{bg=}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{\textdbend\,\,\,doがあったりなかったり}
 \begin{enumerate}
  \item<1-> \begin{enumerate}
	 \item<1-> \myAnch{focus_1}{Maroon}{She} teaches music.\\
\mbox{}\\
\mbox{}
	 \item<2-> \myAnch{wh_1}{Maroon}{Who} teaches music?
	\end{enumerate}
  \item<3-> \begin{enumerate}
	 \item<3-> She teaches \myAnch{focus_2}{NavyBlue}{music}.\\
\mbox{}\\
\mbox{}
	 \item<4-> \myAnch{wh_2}{NavyBlue}{What} does she teach?
	\end{enumerate}
 \end{enumerate}

\begin{tikzpicture}[remember picture, overlay]
\visible<2->{\draw[->, line width=3pt,opacity=.5, Maroon] (focus_1.south) to[out=-90, in=90]  node[sloped,above,text=black,font=\tiny,pos=.667]{} (wh_1.north);}
\visible<4->{\draw[->, line width=3pt,opacity=.5, NavyBlue] (focus_2.south) to[out=-90, in=60]  node[sloped,above,text=black,font=\tiny,pos=.667]{先頭へ} (wh_2.north);}
\end{tikzpicture}


\begin{block}<5->{Topics for Today}
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item もともと先頭にあったとき$\rightarrow$疑問詞にするだけ
 \item もともと先頭になかったとき$\rightarrow$疑問詞にしてから
       \begin{itemize}
	\item その疑問詞を先頭に置く
	\item さらに、そのあとを\,\,\Circled[fill color = white]{\,\,do(does) $+$ S $+$ 原形\,\,}\,\,にします
       \end{itemize}
\end{itemize}
 
\end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
\textdbend\,\,\,つぎの各文の意味をかんがえましょう

\begin{enumerate}
 \item \begin{enumerate}
		  \item Who loves you?\hfill{}cf. She loves you.
		  \item Who do you love?\hfill{}cf. You love Pat. 
		 \end{enumerate}
 \item \begin{enumerate}
	\item Carelessness causes accidents.\hfill{\scriptsize carelessness \textipa{/k\'e\textrhookschwa l@sn@s/} 不注意}
	\item What causes accidents?\hfill{\scriptsize cause \textipa{/k\'O:z/} 引き起こす}
       \end{enumerate}
 \item \begin{enumerate}
	\item You eat bread for breakfast.
	\item What do you eat for breakfast?
       \end{enumerate}
\end{enumerate}
\hfill{\scriptsize \myaudio{./audio/020a_wh_02.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
