\documentclass[aspectratio=169,xcolor={dvipsnames,table}]{beamer}
\usepackage[no-math,deluxe,haranoaji]{luatexja-preset}
\renewcommand{\kanjifamilydefault}{\gtdefault}
\renewcommand{\emph}[1]{{\upshape\bfseries #1}}
\usetheme{metropolis}
\metroset{block=fill}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{blocks}[rounded][shadow=false]
\usecolortheme[rgb={0.7,0.2,0.2}]{structure}
%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Change alert block colors
%%% 1- Block title (background and text)
\setbeamercolor{block title alerted}{fg=mDarkTeal, bg=mLightBrown!45!yellow!45}
\setbeamercolor{block title example}{fg=magenta!10!black, bg=mLightGreen!60}
%%% 2- Block body (background)
\setbeamercolor{block body alerted}{bg=mLightBrown!25}
\setbeamercolor{block body example}{bg=mLightGreen!15}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{myPreamble4Slide.tex}
\usepackage{pxrubrica}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% リエゾン
\newcommand{\liaison}[1][black]{% 引数1を受け取る。デフォルト値はblack
  \tikz[baseline=0pt] \draw[draw=#1,line width=.6pt] (0,0) to[bend right=20] (0.2,0);%
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{English is fun.}
\subtitle{お茶をいかがですか}
\author{}
\institute[]{}
\date[]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% TEXT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{frame}[plain]
  \titlepage
\end{frame}

%\section*{授業の流れ}
%\begin{frame}[plain]
%  \frametitle{授業の流れ}
%  \tableofcontents
%\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{～がほしい}
\large
 \begin{enumerate}
  \item<1-> \textbf{I want} some tea.\hfill{\scriptsize \textipa{/w\'Ant/}}
  \item<2-> \textbf{I would like} some tea.\hfill{\scriptsize \textipa{/w@d laIk/}}
  \item<3-> {\bfseries I'd like} some tea.
 \end{enumerate}

\begin{block}<4->{Topics for Today}\small
\textbf{I would like} $+$ 名詞\,\ldots\,\,.\,\,は\textbf{I want} $+$ 名詞\,\ldots\,\,.\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{I want} $+$ 名詞\,\ldots\,\,.
 \item \textbf{I would like} $+$ 名詞\,\ldots\,\,.
 \item \textbf{I'd like} $+$ 名詞\,\ldots\,\,.
       \end{itemize}
\end{block}

\hfill{\scriptsize \myaudio{./audio/041_would_like_01.mp3}}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
次の英文をI would likeまたはI'd likeをもちいて、 ていねいな表現にしてみましょう
 \begin{enumerate}
  \item I want some water.\\
\visible<2->{$\longrightarrow$ \textbf{I would like} some water.}\\
\visible<3->{$\longrightarrow$ \textbf{I'd like} some water.}
  \item I want a sandwich.\hfill{\scriptsize sandwich \textipa{/s\'\ae n(d)wItS/}}\\
\visible<4->{$\longrightarrow$ \textbf{I would like} a sandwich.}\\
\visible<5->{$\longrightarrow$ \textbf{I'd like} a sandwich.}
  \item I want some flowers for my birthday.\\
\visible<6->{$\longrightarrow$ \textbf{I would like} some flowers for my birthday.}\\
\visible<7->{$\longrightarrow$ \textbf{I'd like} some flowers for my birthday.}
 \end{enumerate}

\hfill{\scriptsize \myaudio{./audio/041_would_like_02.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{～したい}
\large
 \begin{enumerate}
  \item<1-> \textbf{I want to} eat a hamburger.\hfill{\scriptsize hamburger \textipa{/h\'\ae mb\textrhookschwa :g\textrhookschwa/}}
  \item<2-> \textbf{I would like to} eat a hamburger.\hfill{\scriptsize \textipa{/w@d laIk t@/}}
  \item<3-> {\bfseries I'd like to} eat a hamburger.
 \end{enumerate}

\begin{block}<4->{Topics for Today}\small
\textbf{I want to} $+$ 原形\,\,は「～したい」という意味

\textbf{I would like to} $+$ 原形\,\ldots\,\,.\,\,は\textbf{I want to} $+$原形\,\ldots\,\,.\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{I want to} $+$ 原形\,\ldots\,\,.
 \item \textbf{I would like to} $+$ 原形\,\ldots\,\,.
 \item \textbf{I'd like to} $+$ 原形\,\ldots\,\,.
       \end{itemize}
\end{block}

\hfill{\scriptsize \myaudio{./audio/041_would_like_03.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
次の英文をI would likeまたはI'd likeをもちいて、 ていねいな表現にしてみましょう
 \begin{enumerate}
  \item I want to visit London.\hfill{\scriptsize London \textipa{/l\'\textturnv nd@n/}}\\
\visible<2->{$\longrightarrow$ \textbf{I would like to} visit London.}\\
\visible<3->{$\longrightarrow$ \textbf{I'd like to} visit London.}
  \item I want to read a book.\\
\visible<4->{$\longrightarrow$ \textbf{I would like to} read a book.}\\
\visible<5->{$\longrightarrow$ \textbf{I'd like to} read a book.}
  \item I want to play tennis.\\
\visible<6->{$\longrightarrow$ \textbf{I would like to} play tennis.}\\
\visible<7->{$\longrightarrow$ \textbf{I'd like to} play tennis.}
 \end{enumerate}
\hfill{\scriptsize \myaudio{./audio/041_would_like_04.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{～がほしいですか、～はいかがですか}
\large
 \begin{enumerate}
  \item<1-> \textbf{Do you want} some coffee?\hfill{\scriptsize cf. I want some coffee.}
  \item<2-> \textbf{Would you like} some coffee? \hfill{\scriptsize cf. I would like some coffee.}
 \end{enumerate}

\bigskip

\begin{block}<3->{Topics for Today}\small
\textbf{Would you like \ldots\,?}\,\,は\textbf{Do you want \ldots\,?}\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{Do you want} $+$ 名詞 \ldots\,?
 \item \textbf{Would you like} $+$ 名詞 \ldots\,?
       \end{itemize}
\end{block}
\hfill{\scriptsize \myaudio{./audio/041_would_like_05.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
次の英文を would you likeをもちいて、 ていねいな表現にしてみましょう
 \begin{enumerate}
  \item Do you want a pizza?\\
\visible<2->{$\longrightarrow$ \textbf{Would you like} a pizza?}\\
  \item Do you want some juice?\\
\visible<3->{$\longrightarrow$ \textbf{Would you like} some juice?}\\
  \item What do you want for dinner?\\
\visible<4->{$\longrightarrow$ What \textbf{would you like} for dinner?}\\
 \end{enumerate}

\hfill{\scriptsize \myaudio{./audio/041_would_like_06.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{～したいですか、～しませんか}
\large
 \begin{enumerate}
  \item \textbf{Do you want to} watch a movie?
  \item \textbf{Would you like to} watch a movie?
 \end{enumerate}

\begin{block}{Topics for Today}\small
\textbf{Would you like to} $+$ 原形\,\,\ldots\,?\,\,は\,\,\textbf{Do you want to} $+$原形\,\,\ldots\,?\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{Do you want to} $+$ 原形 \ldots\,?
 \item \textbf{Would you like to} $+$ 原形 \ldots\,?
       \end{itemize}
\end{block}
\hfill{\scriptsize \myaudio{./audio/041_would_like_07.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
日本語の意味になるよう(~~~~~~)内の語句を並べ替えてください。先頭に来る語は大文字で始めてましょう。なお[$+1$]とある場合は1語補ってください

 \begin{enumerate}
  \item わたしたちといっしょに動物園に行きたいですか。（行きませんか）\\
( go / like / you / to / to / with / would / the zoo ) us?\\
\visible<2->{\textbf{Would you like to} go to the zoo with us?}
  \item あなたはなにをお飲みになりますか。\\
( like / drink / you / to / would / what ) ?\\
\visible<3->{What \textbf{would you like to} drink?}
  \item パーティーにきたいですか。（きませんか）\\
( you / the party / come / like / to / would ) ? [$+1$]\\
\visible<4->{\textbf{Would you like to}} \visible<5->{come to the party?}
\end{enumerate}
\hfill{\scriptsize \myaudio{./audio/041_would_like_08.mp3}}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{まとめ}
 \begin{block}{～がほしい}\small
\textbf{I would like} $+$ 名詞\,\ldots\,\,.\,\,は\,\,\textbf{I want} $+$ 名詞\,\ldots\,\,.\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{I want} $+$ 名詞\,\ldots\,\,.\hfill{\scriptsize \textbf{I want} some tea.}
 \item \textbf{I would like} $+$ 名詞\,\ldots\,\,.\hfill{\scriptsize \textbf{I would like} some tea.}
 \item \textbf{I'd like} $+$ 名詞\,\ldots\,\,.\hfill{\scriptsize \textbf{I'd like} some tea.}
       \end{itemize}
\end{block}

\begin{block}{～したい}\small
\textbf{I would like to} $+$ 原形\,\ldots\,\,.\,\,は\,\,\textbf{I want to} $+$原形\,\ldots\,\,.\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{I want to} $+$ 原形\,\ldots\,\,.\hfill{\scriptsize \textbf{I want to} have some tea.}
 \item \textbf{I would like to} $+$ 原形\,\ldots\,\,.\hfill{\scriptsize \textbf{I would like to} have some tea.}
 \item \textbf{I'd like to} $+$ 原形\,\ldots\,\,.\hfill{\scriptsize \textbf{I'd like to} have some tea.}
       \end{itemize}
\end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{Exercises}
つぎの英文を読み、設問に答えましょう
 \begin{tcolorbox}[colframe=NavyBlue!20,
  colback=NavyBlue!10!white,
  colbacktitle=NavyBlue!40!white,
  coltitle=black, fonttitle=\bfseries,
  title=A Day at the Park]
I would like to go to the park this Saturday. The weather will be nice. I can see many people there. Some are walking their dogs. Some are playing football. There are children on the swings. I would like to play football with my friends. After that, we will eat ice cream. I hope it will be a wonderful day. Do you want to go to the park with me?
\end{tcolorbox}
The person wants to go to the park on Saturday. (True/False)
The person plans to play football at the park. (True/False)
The person will eat pizza after playing. (True/False)
There are children playing on the swings. (True/False)
The person invites you to go to the park. (True/False)

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{まとめ}
\begin{block}{～がほしいですか、～はいかがですか}\small
\textbf{Would you like} $+$ 名詞\,\ldots\,\,?\,\,は\,\,\textbf{Do you want} $+$ 名詞\,\ldots\,\,?\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{Do you want} $+$ 名詞 \ldots\,?\hfill{\scriptsize \textbf{Do you want} some tea?}
 \item \textbf{Would you like} $+$ 名詞 \ldots\,?\hfill{\scriptsize \textbf{Would you like} some tea?}
       \end{itemize}
\end{block}

\begin{block}{～したいですか、～しませんか}\small
\textbf{Would you like to} $+$ 原形\,\ldots\,?\,\,は\,\,\textbf{Do you want to} $+$原形\,\ldots\,?\,\,のていねいな表現です
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item \textbf{Do you want to} $+$ 原形\,\ldots\,?\hfill{\scriptsize \textbf{Do you want to} eat lunch together?}
 \item \textbf{Would you like to} $+$ 原形\,\ldots\,?\hfill{\scriptsize \textbf{Would you like to} eat lunch together?}
       \end{itemize}
\end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{ところで}
 \begin{enumerate}
  \item<1-> I want \fbox{\,\,\,\,\,\,\,\,\,\,{$x$}\,\,\,\,\,\,\,\,\,\,}\,\,.
  \item<2-> I want some cookies.\hfill{\scriptsize $X = \text{some cookies}$}
  \item<3-> I want to make some cookies.\hfill{\scriptsize $X = \text{to make some cookies}$}
 \end{enumerate}

\vfill

\begin{block}<4->{}
 
\textdbend \textdbend
\begin{itemize}\setbeamertemplate{items}[square]\small
 \item wantには名詞が続く場合と\,\,\Circled[fill color = white]{\,\,to$+$原形\,\,}\,\,が続く場合があります
 \item would likeも同じです
\end{itemize}
\end{block}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}[plain]{want toの発音}
 \begin{enumerate}
  \item I \textbf{want to} see you.
  \item I \textbf{want to} play soccer.
  \item I \textbf{want to} go to the park.
  \item I \textbf{want to} read this book.
  \item I \textbf{want to} drink some water.
 \end{enumerate}

 \begin{block}{want to}\small
%want\tikz[baseline] \draw[line width=.7pt, color=Maroon] (0,0) .. controls (0.1,-0.08) and (0.3,-0.08) .. (0.4,0);to


want\liaison[Maroon]to

  \begin{itemize}\setbeamertemplate{items}[square]\small
   \item \textipa{/wAn@/}と発音されることがあります
  \end{itemize}
 \end{block}


\hfill{\scriptsize \myaudio{./audio/041_would_like_09.mp3}}

\end{frame}
\end{document}
