%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
001_there_is__01.mp3
1. There ( are ) three high schools in our city.
2. There ( is ) a new computer on the desk.
3. There ( are ) two boys in the park this morning.
4. There ( is ) a cat by the tree now.
5. There ( is ) a station near my house.
<speak>
<p>Hello everyone. Please listen carefully as I read the example sentences.</p>
<p><lang xml:lang="ja-JP">さあ、実際の音声によく耳をかたむけてください。それでは、始めます。</lang>Please listen carefully.</p>
<p>Number 1. There are three high schools in our city. <break time="2s"/>There are three high schools in our city.<break time="3s"/></p>
<p>Number 2. There is a new computer on the desk. <break time="2s"/>There is a new computer on the desk.<break time="3s"/></p>
<p>Number 3. There are two boys in the park this morning. <break time="2s"/>There are two boys in the park this morning.<break time="3s"/></p>
<p>Number 4. There is a cat by the tree now. <break time="2s"/>There is a cat by the tree now.<break time="3s"/></p>
<p>Number 5. There is a station near my house. <break time="2s"/>There is a station near my house.<break time="3s"/></p>
<p><lang xml:lang="ja-JP">さあ、いかがでしたか。こんどは、わたしのあとに続けて実際にリピートしてください。</lang>Please repeat after me.</p>
<p>Number 1.  There are three high schools in our city. <break time="5s"/>There are three high schools in our city.<break time="3s"/></p>
<p>Number 2.  There is a new computer on the desk. <break time="5s"/>There is a new computer on the desk.<break time="3s"/></p>
<p>Number 3.  There are two boys in the park this morning. <break time="5s"/>There are two boys in the park this morning.<break time="3s"/></p>
<p>Number 4.  There is a cat by the tree now. <break time="5s"/>There is a cat by the tree now.<break time="3s"/></p>
<p>Number 5.  There is a station near my house. <break time="5s"/>There is a station near my house.<break time="3s"/></p>
<p>Good job, everyone! That's all for our pronunciation practice.</p>
</speak>
